|

### 2020-06-19 appendix/appendix.Rmd
cleaning up

---
title: |
       | Supplementary Materials for "The Effect of Legislature Size on Public Spending: A Meta-Analysis"
author: 
- "Huzeyfe Alptekin[^alptekin]"
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
- "Catarina Roman[^roman]"
date: June 13, 2020
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

@@

```{r, include=FALSE}
# Knitr options
knitr::opts_chunk$set(fig.pos = 'H') # holds figure position
knitr::opts_chunk$set(echo = TRUE)
```

@@

# Needed packages
pkgs <- c('tidyverse', 'meta', 'metafor', 
          'readxl', 'compareGroups',
          'knitr', 'gridGraphics', 'gridExtra',
          'ggpubr','kableExtra','magick')

# Install if not already installed
installIfNot <- function(x) {
  if(x %in% rownames(installed.packages()) == FALSE) 
    install.packages(x, dependencies = T, repos = "http://cran.us.r-project.org")
} 
lapply(pkgs, installIfNot)

@@

# Load datasets
load('../dataset/dataCoefs.RData')

@@

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2,TE), 
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group), 
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1*limg, 1.1*limg)) +
    scale_y_discrete(
      labels = function(x) 
        str_replace(x, "_[0-9]*$", "")) + 
    geom_vline(xintercept=0, 
               color="#000000", linetype="dashed") +
    labs(x = "",
         y = "") + 
    facet_grid(group~., scales = "free", space = "free") + 
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8*lsize, 
                                     hjust = 1),
          axis.text.x = element_text(size = .6*lsize, 
                                     hjust = 1.1),
          plot.caption = element_text(size=lsize),
          plot.title.position = 'plot', 
          plot.title = element_text(hjust = 0.5, 
                                    face = 'bold',
                                    margin=margin(0,0,10,0)),
          panel.grid.major = element_blank())
  return(p)
}
```

@@

The first step in reviews is to gather a sample of records. This initial procedure is the foundation for the entire meta-analytical process: if the goal is to aggregate all the available data on a given topic, the primary pool must encompass all of it. At the same time, the sample should be concise enough to optimise the work flow. Upon selecting the online databases, we attempted to do a "term" search, based on a set of words we scouted from the distributive politics literature we already knew. This search produced oversized databases, of which a large share was completely unrelated to our subject of investigation. The strategy we found to be the most thorough and productive was to select the records that cited Weingast, Shepsle and Johnsen's 1981 paper "The political economy of benefits and costs: A neoclassical approach to distributive politics". Although \href{https://scholar.google.com/}{Google Scholar} reports the article amounts to \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations\footnote{As of May 11\textsuperscript{th}, 2020.}, as of the 21\textsuperscript{st} of November 2019, our search resulted in a total of 2,664 records.

We webscraped the main databases in Social Sciences: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and \href{https://www.scopus.com/}{Scopus} (n = 736). The R script we wrote extracted, to a CSV file, the title, abstract, authors, year, journal of publication, and database from which the record originated. We screened these results with an English language and Article restriction -- meaning, we excluded all records written in other languages and all that were not academic papers, such as book chapters, doctoral theses, etc. We set no restriction to unpublished articles.

@@

The selection process was conducted by two authors in three phases. In the first round, we excluded all titles that were obviously unrelated to our topic. For instance, we curiously found articles about automobile motors amidst our sample. We consider this a preliminary step, since we were not able to eliminate a large number of entries. Thus, we read all abstracts. We chose to maintain those that indicated either government expenditure or legislative structures were central matters. For instance, if the paper sought to identify variables that increased government size, it was maintained. Abstracts that indicated the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics, for example, were also included. This allowed us to significantly reduce our sample to 376 records.

In the second phase, we assessed full-texts. To proceed, the paper should (i) conduct a quantitative analysis, (ii) report data on the number of legislators, and (iii) also on public expenditure. If the record was marked as positive for all three, it was maintained. Disagreements in this phase were discussed among the authors, and a third was consulted when needed.

The third phase consisted of filling out tables for each of the remaining 50 articles to systematically evaluate their eligibility. Since government spending and the number of parliamentaries assume the form of different variables, we extracted the coefficients that provided this information in all papers, indicating and defining which variables each author used. By observing what is most commonly used, we could decide which variables we would employ in our analysis. In this phase, we also collected information on whether or not the paper had been published, and if it explicitly discussed the \textit{law of 1/n}. Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of 26 articles.

@@

1. Matched treatment variable:
  + *N*: Number Legislators Lower House
  + *logN*: Log Number Legislators Lower House
  + *K*: Number Legislators Upper House

@@

We visually organised the flow of articles across eligibility phases through this diagram\footnote{According to the \href{www.prisma-statement.org/}{PRISMA} statement for reporting meta-analyses and systematic reviews}. The column to the right depicts the amount of articles excluded in each phase, and the one to the left shows the number of records evaluated.

@@

The meta-analytic data is comprised of two datasets. The first has the main coefficients that were reported in the paper. It includes only the most rigorous model from each paper, that is, those estimated with the largest $n$, most control variables, and fixed effects if the authors added them. If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one. This sample encompasses 36 estimates, as 10 articles analysed two dependent or independent variables of interest. Our second sample, in contrast, contains all the 126 effect sizes reported in the 26 papers.

In the main text, we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended set. Below is the data extraction process for all relevant coefficients in the selected articles. In the Meta-Analysis and Meta-Regressions sections of this Appendix, you will find all tests performed in both reduced and full samples.

@@

In this section, we present the descriptive statistics for our meta-analytic sample. We focus in the following paper characteristics: study year, whether the paper has been published or not, the three dependent variables of interest, the three independent variables of interest, and a few statistics about the coefficients. We also add a descriptive statistics table, similar to the one in the main paper.

@@

For study year, we have an average of `r round(mean(dat$year), 2)`, with standard deviation of `r round(sd(dat$year), 2)`. The oldest study included in the paper is dated from `r min(dat$year)`, while the most recent paper is dated from `r max(dat$year)`. Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the 1/n hypothesis.

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Study Year Frequencies"}
dat %>%
  select(id, year) %>%
  unique() %>%
  ggplot(aes(x = as.factor(year))) + 
    geom_bar(color = "black") + 
  labs(x = "",
       y = "") + 
  theme_bw()
```

@@

We decided to report studies regardless of their publication status. From the `r length(unique(dat$id))` papers in the sample, `r as.numeric(table(unique(select(dat, id, published))$published)[1])` were published while `r as.numeric(table(unique(select(dat, id, published))$published)[2])` were not published.

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
dat %>%
  select(id, published) %>%
  unique() %>%
  ggplot(aes(x = as.factor(published))) + 
    geom_bar(color = "black") + 
  labs(x = "Published Study?",
       y = "") + 
  theme_bw()
```

@@

There are many differences in the papers relative to the research design. One remarkable difference is the application of the theory, that was build with majoritarian systems in mind, to non-majoritarian democracies. In our sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that the argument for working in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographycally concentrated. The concentration facilitates politicians to use pork-barrel project to captivate their electoral supporters.}

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Electoral Systems"}
dat %>%
  select(id, elecsys2) %>%
  unique() %>%
  ggplot(aes(x=as.factor(elecsys2))) + 
    geom_bar(color = "black") + 
  labs(x = "Electoral Systems",
       y = "") + 
  theme_bw()
```

@@

The aggregation level is also an important characteristic of the empirical tests of the law of 1/n. The model was build to explain the dynamics of majoritarian countries, but the theory was tested in municipal, county, states, and country levels. In our sample, `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[1])` studied *local* level (municipalities and counties), `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[2])` studied *State* (or Provincial) levels, and `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[3])` studied *Country* level data.

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Sample Aggregate Level"}
dat %>%
  select(id, agglevel) %>%
  unique() %>%
  ggplot(aes(x=as.factor(agglevel))) + 
    geom_bar(color = "black") + 
  labs(x = "Sample Aggregate Level",
       y = "") + 
  theme_bw()
```

@@

The outcome variables included in the paper were:

@@

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Dependent variables across the law of 1/n studies"}
dat %>%
  select(id, depvar2) %>%
  unique() %>%
  mutate(depvar2 = factor(depvar2, 
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") + 
  labs(x = "Dependent Variables",
       y = "") + 
  coord_flip() + 
  theme_bw()
```

@@

Most of papers in our meta-analytic sample study the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[2])`). The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[1])`). Finally, the minority of papers study the Natural Log of the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[3])`). Some papers had multiple coefficients, and thus the total number of coefficients is 36, while the number of papers is only 26.

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Independent variables across the law of 1/n studies"}
dat %>%
  select(id, indepvar2) %>%
  unique() %>%
  mutate(indepvar2 = factor(indepvar2, labels = c('K (upper house legislators)',
                                                  'N (lower house legislators)',
                                                  'Log N'))) %>%
  ggplot(aes(x = indepvar2)) + 
    geom_bar(color = "black") + 
  labs(x = "Independent Variables",
       y = "") +
  coord_flip() +
  theme_bw() 
```

@@

```{r, echo=FALSE}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") + 
  labs(x = "Coefficients") + 
  theme_bw()
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") + 
  labs(x = "Standard Errors") + 
  theme_bw()
```

@@

One simple statistic that we can compute to access the law of 1/n is the frequency of positive and negative estimates. Below we plot the frequency for all the papers included in the meta-analytic dataset.

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign"}
dat %>%
  ggplot(aes(x=as.factor(scoef))) + 
  geom_bar(color = "black") + 
  labs(x = "Coefficient Sign",
       y = "") +
  theme_bw()
```

@@

```{r, echo=F,warning=F,message=F}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c('Other Coefficients', 'Main Coefficients')
aux <- select(fulldat, usemeta2, indepvar2, year, published, 
              elecsys2, method, agglevel) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year, 
         `Published work` = published, 
         `Electoral system` = elecsys2, 
         `Estimation method` = method, 
         `Sampling Aggregation Level` = agglevel)

#export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
#                     show.p.overall = F, show.all = T),
#          caption = "Descriptive Statistics of Moderators")

@@

The law of 1/n poses we should have a positive influence of legislature size on expenditure. A general test of the theory could investigate whether the papers tend to find a higher frequency of positive coefficients. In statistical terms, consider a random variable representing the coefficient sign for the papers. As each sign of the paper is a Bernoulli trial, the aggregate for all papers follow a Binomial distribution, with parameters $n$ equals the number of papers, and $p$ the  chance of a positive sign. The law of 1/n can be reformulated as the chance of $p>0.5$, which facilitates the testing of the theory. The null hypothesis for such a test is that:

@@

As we are taking an agnostic approach, we acknowledge that either the law of 1/n ($p>0.5$), or the reverse law of 1/n ($p<0.5$), could be true. In this case, the alternative hypothesis is $p\neq 0.5$. To perform this test, we run binomial tests in R, using the function `binom.test(.)`.

This test has two advantages. First, it is robust to the design of the paper. As papers select different types of journals, countries, samples, and other characteristics, this increases the heterogeneity. This test ignores the design discrepancies and focus on the overall effect. Second, this test has the advantage of be simple and straightfoward. It requires very few assumption and has a direct statistical formulation. The disadvantage is that we can extract more information with meta-regressions.

@@

```{r, echo=FALSE}
aux <- filter(dat, indepvar2=='N')
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
aux2
```

@@

```{r, echo=FALSE}
aux <- filter(dat, indepvar2=='logN')
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
aux2
```

@@

```{r, echo=FALSE}
aux <- filter(dat, indepvar2=='K')
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
aux2
```

@@

We combined the three independent ($N$, $\log(N)$, and $K$) with the levels of the three dependent variables (Expenditure Per Capita, Log of Expenditure Per Capita, Expenditure as a Percentage of the GDP). This formed a 3x3 possibility for our analysis.

@@

```{r, echo=FALSE}
# Pooling effects analysis -- ExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
build_forest(mod, NULL)
```

```{r,include=F,warning=F}
f1 <- build_forest(mod, NULL, lsize = 15, ttl = 'Lower House Size\nand Expenditure per Capita')
```

@@

1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

@@

The law of 1/n was created for majoritarian systems. In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a binary electoral system.

```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE}
mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)

@@

```{r}
# Pooling effects analysis -- ExpPC x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

@@

```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
build_forest(mod, NULL)
```

@@

```{r}
# Pooling effects analysis -- logExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

>>>>

---
title: |
       | Supplementary Materials for "The Effect of Legislature Size on Public Spending: A Meta-Analysis"
author:
- "Huzeyfe Alptekin[^alptekin]"
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
- "Catarina Roman[^roman]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

@@

```{r, include=FALSE}
# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)
```

@@

# Needed packages
pkgs <- c("tidyverse", "meta", "metafor",
          "readxl", "compareGroups",
          "knitr", "gridGraphics", "gridExtra",
          "ggpubr", "kableExtra", "magick")

# Install if not already installed
installIfNot <- function(x) {
  if (x %in% rownames(installed.packages()) == FALSE)
    install.packages(x, dependencies = T,
					 repos = "http://cran.us.r-project.org")
}
lapply(pkgs, installIfNot)

@@

# Load datasets
load("../dataset/dataCoefs.RData")

@@

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2, TE),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(group~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}
```

@@

The first step in our systematic review consisted in gathering a study sample. We started our data collection with a manual search based on a set of keywords we scouted from the distributive politics literature. This search produced a database with many entries that were unrelated to our subject of investigation. To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics", which is a seminal contribution in the field. Although \href{https://scholar.google.com/}{Google Scholar} reports the article amounts to \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations\footnote{As of May 11\textsuperscript{th}, 2020.}, our search resulted in 2,664 records as of the 21\textsuperscript{st} of November 2019.

We webscraped three large academic databases: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and \href{https://www.scopus.com/}{Scopus} (n = 736). The `R` script we wrote extracted the article title, abstract, authors, year, journal of publication, and database from which the record originated. Our code is available in section \ref{sub:scrap} below. We screened these results with an English language and article restriction, that is, we excluded all records written in other languages and all that were not academic papers, such as book chapters or doctoral theses. We set no restriction to unpublished articles.

@@

The selection process was conducted by two authors in three phases. In the first round, we excluded all titles that were obviously unrelated to our topic. For instance, we curiously found articles about automobile motors amidst our sample. We consider this a preliminary step, since we were not able to eliminate a large number of entries. Thus, we read all abstracts. We chose to maintain those which indicated that either government expenditure or legislative structures were the main subject of the paper. For instance, if the paper sought to identify variables that increased government size, it was maintained. Abstracts that indicated the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics were also included. This allowed us to significantly reduce our sample to 376 records.

In the second phase, we assessed full texts. To remain in our sample, the paper should (i) conduct a quantitative analysis, (ii) report data on the number of legislators, and (iii) also on public expenditure. If the record was marked as positive for all three, it was maintained. Disagreements in this phase were discussed among the authors, and a third investigator was consulted when needed.

The third phase consisted of filling out tables for each of the remaining 50 articles to systematically evaluate their eligibility. Since authors use different measures for government spending and the number of lower/upper house members, we extracted all coefficients that provided this information. We decided which variables to keep by following the current practices of the literature. In this phase, we also collected information on whether or not the paper had been published, and if it explicitly discussed the \textit{law of 1/n}. Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of 26 articles.

@@

1. Matched treatment variable:
  + *N*: Number Legislators in the Lower House
  + *logN*: Log Number Legislators in the Lower House
  + *K*: Number Legislators in the Upper House

@@

The diagram below shows each step of our article selection process. We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) statement to conduct our study\footnote{More information about the PRISMA statement is available at \url{http://www.prisma-statement.org}.}. The column to the right depicts the amount of articles excluded in each phase, and the one to the left shows the number of records evaluated.

@@

The meta-analytic data is comprised of two datasets. The first dataset has the main coefficients reported in the studies. These data include only the most rigorous model from each paper, that is, those estimated with the largest $n$, most control variables, and fixed effects if the authors added them. If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one. This sample encompasses 36 estimates, as 10 articles analysed two dependent or independent variables of interest. Our second sample, in contrast, contains all the 126 effect sizes reported in the 26 papers.

In the main text, we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended set. Below is the data extraction process for all relevant coefficients in the selected articles. Here we present the results of all tests performed in both reduced and full samples.

@@

In this section, we show the descriptive statistics for our meta-analytic sample. We focus on the following paper characteristics: study year, whether the paper has been published or not, the electoral system of the country discussed in the original study, the data aggregation level, as well as the distribution of the dependent and independent variables of interest. We also add a descriptive statistics table similar to the one in the main paper.

@@

For study year, we have an average of `r round(mean(dat$year), 2)`, with standard deviation of `r round(sd(dat$year), 2)`. The oldest study included in the paper is dated from `r min(dat$year)`, while the most recent paper is dated from `r max(dat$year)`. Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the _law of 1/n_.

```{r, fig.width=7, fig.height=3, fig.cap="Study Year Frequencies", cache=TRUE}
dat %>%
  select(id, year) %>%
  unique() %>%
  ggplot(aes(x = as.factor(year))) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "") +
  theme_bw()
```

@@

Studies were included in our sample regardless of their publication status. From the `r length(unique(dat$id))` papers in the sample, `r as.numeric(table(unique(select(dat, id, published))$published)[1])` were published while `r as.numeric(table(unique(select(dat, id, published))$published)[2])` were not published.

```{r, fig.width=4, fig.height=3, fig.cap="Was the study published?", cache=TRUE}
dat %>%
  select(id, published) %>%
  unique() %>%
  ggplot(aes(x = as.factor(published))) +
    geom_bar(color = "black") +
  labs(x = "Published Study?",
       y = "") +
  theme_bw()
```

@@

Our study selection differs considerably in regards to research design. One remarkable difference is that several authors apply the logics of the _law of 1/n_, which was build with majoritarian systems in mind, to non-majoritarian democracies. In our sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that the argument for working in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographically concentrated. The concentration facilitates politicians to use pork-barrel projects to captivate their electoral supporters.}

```{r, fig.width=4, fig.height=3, fig.cap="Electoral Systems", cache=TRUE}
dat %>%
  select(id, elecsys2) %>%
  unique() %>%
  ggplot(aes(x=as.factor(elecsys2))) +
    geom_bar(color = "black") +
  labs(x = "Electoral Systems",
       y = "") +
  theme_bw()
```

@@

The aggregation level is also an important characteristic of the empirical tests of the _law of 1/n_. While the original model was build to explain the dynamics of majoritarian countries, the theory has been tested at the municipal, county, states, and country levels. In our sample, `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[1])` analysed data from the *local* level (municipalities and counties), `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[2])` studied the *state* (or Provincial) level, and `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[3])` used *country* level data.

```{r, fig.width=4, fig.height=3, fig.cap="Sample Aggregate Level", cache=TRUE}
dat %>%
  select(id, agglevel) %>%
  unique() %>%
  ggplot(aes(x=as.factor(agglevel))) +
    geom_bar(color = "black") +
  labs(x = "Sample Aggregate Level",
       y = "") +
  theme_bw()
```

@@

The outcome variables included in the paper are:

@@

```{r, fig.width=4, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", cache=TRUE}
dat %>%
  select(id, depvar2) %>%
  unique() %>%
  mutate(depvar2 = factor(depvar2,
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") +
  labs(x = "Dependent Variables",
       y = "") +
  coord_flip() +
  theme_bw()
```

@@

Most of papers in our sample analyse the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[2])`). The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[1])`). Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[3])`). As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is 36, while the number of papers is only 26.

```{r, fig.width=4, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", cache=TRUE}
dat %>%
  select(id, indepvar2) %>%
  unique() %>%
  mutate(indepvar2 = factor(indepvar2, labels = c("K (upper house legislators)",
                                                  "N (lower house legislators)",
                                                  "Log N"))) %>%
  ggplot(aes(x = indepvar2)) +
    geom_bar(color = "black") +
  labs(x = "Independent Variables",
       y = "") +
  coord_flip() +
  theme_bw()
```

@@

Coefficients:

```{r, cache=TRUE, fig.width=5, fig.height=4}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") +
  labs(x = "Coefficients") +
  theme_bw()
```

Standard errors:

```{r, cache=TRUE, fig.width=5, fig.height=4}
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") +
  labs(x = "Standard Errors") +
  theme_bw()
```

@@

One simple statistic that we can compute to assess the validity of the _law of 1/n_ is the frequency of positive and negative estimates in the study sample. Below we plot the frequency for all the papers included in the meta-analytic dataset.

```{r, fig.width=5, fig.height=4, fig.cap="Coefficient Sign", cache=TRUE}
dat %>%
  ggplot(aes(x=as.factor(scoef))) +
  geom_bar(color = "black") +
  labs(x = "Coefficient Sign",
       y = "") +
  theme_bw()
```

@@

```{r, warning=F,message=F, cache=TRUE}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
aux <- select(fulldat, usemeta2, indepvar2, year, published,
              elecsys2, method, agglevel) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year,
         `Published work` = published,
         `Electoral system` = elecsys2,
         `Estimation method` = method,
         `Sampling Aggregation Level` = agglevel)

@@

The _law of 1/n_ posits that we should expect a positive influence of legislature size on public expenditures. A general test of the theory could investigate whether the papers tend to find a higher frequency of positive coefficients in their estimations. In statistical terms, consider a random variable representing the coefficient sign for the papers. As each sign of the paper is a Bernoulli trial, the aggregate result for all papers follows a Binomial distribution with parameters $n$ equals the number of papers, and $p$ the  chance of a positive sign. The _law of 1/n_ can be reformulated as the chance of $p>0.5$, which facilitates the testing of the theory. The null hypothesis for such a test is that:

@@

As we are taking an agnostic approach, we acknowledge that either the _law of 1/n_ ($p>0.5$), or the _reverse law of 1/n_ ($p<0.5$) could be true. In this case, the alternative hypothesis is $p\neq 0.5$. To perform this test, we run binomial tests in `R`, using the function `binom.test(.)`.

This test has two advantages. First, it is robust to the design of the paper. This is an important feature as papers analyse different countries, samples, and have distinct characteristics, such as whether they were published or not. All these factors increase the levels of study heterogeneity. The binomial test ignores the design discrepancies and focuses on the overall reported effect. Second, this test has the advantage of being straightforward and easy to interpret. It requires very few assumption and has a direct statistical formulation. The disadvantage is that we can extract more information from the articles with meta-regressions, as we see in the next sections.

@@

```{r, cache=TRUE}
aux <- filter(dat, indepvar2 == "N")
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
aux2
```

@@

```{r, cache=TRUE}
aux <- filter(dat, indepvar2 == "logN")
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
aux2
```

@@

```{r, cache=TRUE}
aux <- filter(dat, indepvar2=='K')
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
aux2
```

@@

## Estimation Method

In general terms, there are two main ways to conduct a meta-analysis, using fixed effects or random effects models. The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true effect. The random effects model, on the other hand, assumes that there are a distribution of true effects, that vary based on sample and tests characteristics.

In this paper, we use the random effects model. The empirical papers testing the _law of 1/n_ are very diverse. We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:

1. **Subjects**: Counties, Municipalities, States, Provinces, Countries.
2. **Electoral systems**: Majoritarian, PR, Mixed.
3. **Modelling strategies**: Panel data, Standard OLS, IV, RDD.

In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in [Doing Meta-Analysis with R](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html). To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$. We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data.

We combined the three independent variables ($N$, $\log(N)$, and $K$) with our dependent variables of interest (Expenditure Per Capita, Log of Expenditure Per Capita, Expenditure as a Percentage of the GDP). This formed a $3 \times 3$ table, and in the following pages we present the results for each of these combinations.

@@

```{r, cache=TRUE}
# Pooling effects analysis -- ExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

```{r,include=F,warning=F, cache=TRUE}
f1 <- build_forest(mod, NULL, lsize = 15, ttl = 'Lower House Size\nand Expenditure per Capita')
```

@@

1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
2. The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

@@

The _law of 1/n_ was created for majoritarian systems. In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a binary electoral system.

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE, cache=TRUE}
mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)

@@

```{r, cache=TRUE}
# Pooling effects analysis -- ExpPC x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

@@

```{r, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
build_forest(mod, NULL)
```

@@

```{r, cache=TRUE}
# Pooling effects analysis -- logExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')
